NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-10-11 Manuscript/manuscriptPS.tex
Update text

Dilution of PS lipid bilayers with PC lipids reduces the propensity
of PS headgroup-multivalent ion complexes and is proposed to make PS
headgroups less rigid~\cite{browning80,buldt81,roux90,roux91}.
This is related to the shift of the PS headgroup order parameters 
closer to zero when bilayer is diluted with PC
lipids (Fig.~\ref{HGorderparametersPCvsPS})~\cite{browning80,scherer87,roux90}.
%which is intepreted to indicate reduced rigidity~\cite{browning80,buldt81}.
This shift is not seen in CHARM36 and Gromos-CKP simulations when bilayer is
diluted with POPC (Fig. \ref{HGorderparametersPCvsPS}).
In lipid14/17 simulations, the headgroup order parameters of POPS shift closer
to zero when the bilayer is diluted with POPC, but the numerical values of
order parameters are too far from experiments, having also different signs,
for the proper interpretation of the experimental data.
Therefore, the imporvements in force fields are necessary
for accurate studies of interactions between PC and PS headgroups
with MD simulations.
%The $\beta$-carbon order parameter
%increase with increasing amount of PS in CHARMM36 and MacRog simulations in contrast
%to the experimental data.
%The smaller $\alpha$-carbon order parameter increase in both
%simulation models with increasing amount of PS, while it is almost unchanged in experiments.
%The larger $\alpha$-carbon order parameter increase in MacRog and decrease in CHARMM36
%with increasing amount of PS, both model exhibiting a poor agreement with experiments.

>>>>

The headgroup order parameteres of POPS shift closer to zero when bilayer
is diluted with POPC (Fig.~\ref{HGorderparametersPCvsPS}),
which is intereted to indicate less rigid structure of PS headgroups in
the mixture~\cite{browning80,buldt81,roux90,roux91,scherer87}.
This shift is observed only in lipid14/17 simulations
%, the headgroup order parameters of POPS shift closer
%to zero when the bilayer is diluted with POPC,
but the numerical values of order parameters are too far from experiments, having also different signs,
for the proper interpretation of the experimental data.
In CHARM36 and Gromos-CKP simulations, the shift of headgroup order
parameters toward zero are not observed when bilayer
diluted with POPC (Fig. \ref{HGorderparametersPCvsPS}).
Therefore, we conclude that more accurate force fields are necessary
for MD simulation studies of PC-PS headgroup interactions.  
%The $\beta$-carbon order parameter
%increase with increasing amount of PS in CHARMM36 and MacRog simulations in contrast
%to the experimental data.
%The smaller $\alpha$-carbon order parameter increase in both
%simulation models with increasing amount of PS, while it is almost unchanged in experiments.
%The larger $\alpha$-carbon order parameter increase in MacRog and decrease in CHARMM36
%with increasing amount of PS, both model exhibiting a poor agreement with experiments.
